---
title: "zonal_stat"
author: "Lallu Nikerthil Prathapan"
date: "2/27/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages install
```{r}
install.packages("D:/EAGLE/Master_Thesis_Hannes/1/R/packages/exactextractr_0.10.0.tar.gz", repos = NULL, type = "source")
```


```{r}
# List of packages to install
#packages_to_install <- c("exactextracter")

# Install the packages
#install.packages(packages_to_install)
```
#Packages library

```{r}
library(sf)
library(ggplot2)
library(raster)
library(exactextractr)
library(terra)
library(dplyr)
library(gridExtra)
library(tidyr)
library(units)
```


#Zonal statistics for each of the global EO population datasets

#Loading the data of camps

```{r}
url <- "data_camps/idp_camps_224.shp"
sf_data <- st_read(url) 
```
# 1. GHSL DATA
```{r}
ghsl_raster_path<-"D:/EAGLE/Master_Thesis_Hannes/1/ghsl_pop_2020_mollweid_100m/merged_ghsl.tif"
# Read the raster file into R
ghsl_raster <- raster(ghsl_raster_path)

```

```{r}
# Display information about the raster
print(ghsl_raster)
```
```{r}
# Plot the raster
plot(ghsl_raster)
```

#!!!!!!The extract function!!!!!!!!!!!!!!!

```{r}
# function

# weighted sum per polygon (using the size of the pixel covered by the polygon "coverage_fraction")

extract_sum  <-  function(raster, polygon, field){

  polygon $id_tmp <- as.data.frame(polygon)[,field]

  v.exact <- exactextractr::exact_extract(raster, polygon, include_cols = 'id_tmp', max_cells_in_memory=3e+10)

  x <- do.call("rbind",v.exact)

  x[,"gpw"] <- x[, "value"] * x$coverage_fraction

  x_sum <- x %>%

    dplyr::group_by(id_tmp)%>%

    dplyr::summarise_at("gpw", sum, na.rm = TRUE)

polygon <- polygon %>%

    left_join(x_sum, by = "id_tmp")

  rm(x,v.exact,x_sum)

  return(polygon)

}
```


```{r}
# Data
sf_data <- st_read(url) 
polygon_camps <-sf_data

```


```{r}
raster_population <- rast('D:/EAGLE/Master_Thesis_Hannes/1/ghsl_pop_2020_mollweid_100m/merged_ghsl.tif')
```

```{r}
# Call function

polygon_camps <- extract_sum(raster_population, polygon_camps,"Name")

```


#Difference in the population
```{r}


# Subtract N_INDVID from ras_name
polygon_camps$ghsl_difference <- polygon_camps$N_INDVID - polygon_camps$ghsl

# View the resulting data frame with the new "difference" column
print(polygon_camps)

```
#Writing the output of the ghsl extract

```{r}

library(sf)

# Convert the data frame to an sf object
sf_polygon_camps <- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
sf_polygon_camps <- st_zm(sf_polygon_camps, drop = TRUE)

# Export the sf object to a shapefile
st_write(sf_polygon_camps,
 "ghsl_output/polygon_camps_ghsl.shp")

```
GHSL some plot visualisation

```{r}
library(ggplot2)



# Define the ggplot object
ggplot(polygon_camps, aes(fill = ghsl)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of GHSL Values for Camps") +
  theme_minimal()

```
```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = ghsl, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated and survey iom populations",
       x = "Estimated population",
       y = "Iom surveyed population") +
  theme_minimal()
```
```{r}
# Scatter plot with different colors based on Shelt_type
ggplot(polygon_camps, aes(x = ghsl, y = N_INDVID, color = Shelt_type)) +
  geom_point() +
  labs(title = "Comparison between ras_name and N_INDVID",
       x = "ras_name",
       y = "N_INDVID") +
  theme_minimal()
```

```{r}
# Scatter plot comparing N_INDIVID and N_HH
plot1 <- ggplot(polygon_camps, aes(x = N_INDVID, y = N_HH, color = ghsl)) +
  geom_point() +
  labs(title = "Comparison between N_INDVID and N_HH",
       x = "N_INDVID",
       y = "N_HH") +
  theme_minimal()

# Scatter plot comparing N_INDIVID and ras_name
plot2 <- ggplot(polygon_camps, aes(x = N_INDVID, y = ghsl, color = ghsl)) +
  geom_point() +
  labs(title = "Comparison between N_INDVID and ghsl",
       x = "N_INDVID",
       y = "ghsl") +
  theme_minimal()

# Scatter plot comparing N_HH and ras_name
plot3 <- ggplot(polygon_camps, aes(x = N_HH, y = ghsl, color = ghsl)) +
  geom_point() +
  labs(title = "Comparison between N_HH and ghsl",
       x = "N_HH",
       y = "ghsl") +
  theme_minimal()

# Arrange the plots in a grid
grid.arrange(plot1, plot2, plot3, ncol = 2)
```
#2.World POP(constrained)

```{r}
World_pop <- rast('D:/EAGLE/Master_Thesis_Hannes/1/world_pop/nga_ppp_2020.tif')
print(World_pop)
```


```{r}

# Call function

polygon_camps <- extract_sum(World_pop,polygon_camps,"Name")

```
#Difference in the survery_population and world_pop
```{r}
# Assuming you have a column named "N_INDVID" in the polygon_camps data frame
# Adjust the column name if needed

# Subtract N_INDVID from ras_name
polygon_camps$world_pop_difference <- polygon_camps$N_INDVID - polygon_camps$wp_c

# View the resulting data frame with the new "difference" column
print(polygon_camps)

```



#Writing the output of the worldpop unconstrained extract

```{r}
# Convert the data frame to an sf object
sf_polygon_camps2 <- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
sf_polygon_camps2 <- st_zm(sf_polygon_camps2, drop = TRUE)

# Export the sf object to a shapefile
st_write(sf_polygon_camps2,
 "world_pop_output/wp_c.shp")

```

#World pop constrained plots
```{r}
# Define the ggplot object
ggplot(polygon_camps, aes(fill = wp_c)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of GHSL Values for Camps") +
  theme_minimal()

```

```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = wp_c, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated_worldpop and survey iom populations",
       x = "Estimated population_worldpop",
       y = "Iom surveyed population") +
  theme_minimal()
```


#3.World POP(unconstrained)

```{r}
World_pop_unconstr <- rast('D:/EAGLE/Master_Thesis_Hannes/1/world_pop_build/nga_ppp_2020_constrained.tif')
print(World_pop_unconstr)

```

```{r}
# Call function

polygon_camps <- extract_sum(World_pop_unconstr,polygon_camps,"Name")

```

#Difference in the survery_population and world_pop unconstrained
```{r}


# Subtract N_INDVID from ras_name
polygon_camps$wp_uc_diff <- polygon_camps$N_INDVID - polygon_camps$wp_uc

# View the resulting data frame with the new "difference" column
print(polygon_camps)
```



#Writing the output of the worldpop unconstrained extract

```{r}
# Convert the data frame to an sf object
poly_camp3<- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
poly_camp3 <- st_zm(poly_camp3, drop = TRUE)

# Export the sf object to a shapefile
st_write(poly_camp3,
 "world_pop_uncons_output/polygon_wpun.shp")



```
#World pop unconstrained plots

```{r}
# Define the ggplot object
ggplot(polygon_camps, aes(fill = wp_uc)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of worldpop constrained Values for Camps") +
  theme_minimal()
```

```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = wp_uc, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated_worldpop_unconstrained and survey iom populations",
       x = "Estimated population_worldpop_unconstrained",
       y = "Iom surveyed population") +
  theme_minimal()
```

#4. GPW_V4

```{r}

gpw <- rast('D:/EAGLE/Master_Thesis_Hannes/1/gpw/gpw-v4-population-count-rev11_2020_30_sec_tif/gpw_v4_population_count_rev11_2020_30_sec.tif')
print(gpw)
```


```{r}
# Call function

polygon_camps <- extract_sum(gpw,polygon_camps,"Name")
```

#Difference in the survery_population and gpw_population
```{r}
# Assuming you have a column named "N_INDVID" in the polygon_camps data frame
# Adjust the column name if needed

# Subtract N_INDVID from ras_name
polygon_camps$gpw_diff <- polygon_camps$N_INDVID - polygon_camps$gpw

# View the resulting data frame with the new "difference" column
print(polygon_camps)
```


#Writing the output of the gpw

```{r}
# Convert the data frame to an sf object
poly_camp4<- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
poly_camp4 <- st_zm(poly_camp4, drop = TRUE)

# Export the sf object to a shapefile
st_write(poly_camp4,
 "gpw/polygon_gpw1.shp")



```
#Gpw plots

```{r}
# Define the ggplot object
ggplot(polygon_camps, aes(fill = gpw)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of worldpop constrained Values for Camps") +
  theme_minimal()
```

```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = gpw, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated_gpw and survey iom populations",
       x = "Estimated population_gpw",
       y = "Iom surveyed population") +
  theme_minimal()
```
#Writing out the whole GHSL, Worldpop(cns),worldpop(uncons),gpw
```{r}
 #Convert the data frame to an sf object
camp_poly_pop<- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
camp_poly_pop <- st_zm(camp_poly_pop, drop = TRUE)

# Export the sf object to a shapefile
st_write(camp_poly_pop,
 "all_pop_output/camp_poly_pop.shp")


```


```{r}
# Select relevant columns
selected_columns <- polygon_camps %>%
  select(id_tmp, ghsl, wp_c, wp_uc, gpw, N_INDVID) %>%
  gather(key = "Variable", value = "Value", -id_tmp)

# Plot
ggplot(selected_columns, aes(x = id_tmp, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  labs(title = "Comparison of Population Variables",
       x = "Camp ID",
       y = "Population",
       fill = "Variable") +
  theme_minimal() +
  theme(axis.text.x)

)
```


#load the data with all the population output to an new variable
```{r}
output_path<-("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/all_pop_output/camp_poly_pop.shp")

output_poly<-st_read(output_path) 
head(output_poly)
```

#5 loading the data from all the building stats

```{r}
build_stat_path<-("D:/EAGLE/Master_Thesis_Hannes/1/R/kml_gee/all_build_stats/all_build_stats.shp")
build_stats_inc<-st_read(build_stat_path)
head(build_stats_inc)
```


#calculating the shape_area of the camp from the geometries of camp_polygons

```{r}

#Calculate the shape area for each camp polygon
build_stats_inc$cal_Shp_area <-st_area(build_stats_inc$geometry)

# Print or view the results
print(build_stats_inc[,c("Name", "cal_Shp_area","Site_Ar")])

# Remove 'units' from the columns
build_stats_inc$cal_Shp_area <- as.numeric(build_stats_inc$cal_Shp_area)
build_stats_inc$Site_Ar <- as.numeric(build_stats_inc$Site_Ar)

# Calculate the difference between 'Calculated_Shape_Area' and 'Site_Ar'
build_stats_inc$Area_Diff <- build_stats_inc$Site_Ar-build_stats_inc$cal_Shp_area

print(build_stats_inc[, c("Name", "cal_Shp_area","Site_Ar","Area_Diff")])
```





# write out the output with the polygon shapearea for surety

```{r}


# Export the sf object to a shapefile
st_write(build_stats_inc,
 "all_pop_output/build_stat_inc.shp")
```

#plot site area of the camps from survey and site area calculated from the digitized

```{r}
# Create a scatter plot
ggplot(build_stats_inc, aes(x = Site_Ar, y = cal_Shp_area)) +
  geom_point(aes(color = "cal_Shp_area"), size = 3) +
  geom_point(aes(color = "Site Area"), size = 1) +
  scale_color_manual(values = c("cal_Shp_area" = "blue", "Site Area" = "red")) +
  labs(title = "Survey_Site Area vs. Calculated Shape Area",
       x = "Survey_Site Area",
       y = "Calculated Shape Area")
```

#plot to check the problem of high population and less area

```{r}
# Create a scatter plot
ggplot(build_stats_inc, aes(x = N_INDVI, y = cal_Shp_area)) +
  geom_point() +
  labs(title = "N_INDVID vs. Calculated Shape Area",
       x = "N_INDVID",
       y = "Calculated Shape Area")
```

```{r}
# Filter camps with high N_INDVID and small cal_Shape_area
check_hipop_lessarea <- build_stats_inc %>%
  filter(N_INDVI > 50)

# Print or view the selected camps
print(selected_camps[, c("Name", "N_INDVI", "cal_Shp_area","Site_Ar")])
```


# the camp values(BO_S294 has the high population of 224 with less area of 342 sq m)
#  Name N_INDVI cal_Shp_area
<!-- 1  AD_S018    75.0   25822.0515 -->
<!-- 2  BO_S294   224.0     342.7668 -->
<!-- 3  AD_S003  1234.0  104062.6921 -->
<!-- 4  BO_S012  3375.0   17558.3622 -->
<!-- 5  BO_S015  1259.0   39288.4634 -->
<!-- 6  BO_S113  5708.0  256595.9877 -->
<!-- 7  BO_S114   739.0   10824.5435 -->
<!-- 8  BO_S160  2500.0  143393.6697 -->
<!-- 9  BO_S162  1260.0   40156.3581 -->
<!-- 10 BO_S203  9223.0  575925.1669 -->






