---
title: "zonal_stat"
author: "Lallu Nikerthil Prathapan"
date: "2/27/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages install
```{r}
install.packages("D:/EAGLE/Master_Thesis_Hannes/1/R/packages/exactextractr_0.10.0.tar.gz", repos = NULL, type = "source")
```


```{r}
# List of packages to install
packages_to_install <- c("hrbrthemes")

# Install the packages
install.packages(packages_to_install)
```
#Packages library

```{r}
library(sf)
library(vctrs)
library(ggplot2)
library(raster)
library(exactextractr)
library(terra)
library(dplyr)
library(gridExtra)
library(tidyr)
library(units)
library(viridis)
library(hrbrthemes)
```


#Zonal statistics for each of the global EO population datasets

#Loading the data of camps

```{r}
url <- "data_camps/idp_camps_224.shp"
sf_data <- st_read(url) 
```
# 1. GHSL DATA
```{r}
ghsl_raster_path<-"D:/EAGLE/Master_Thesis_Hannes/1/ghsl_pop_2020_mollweid_100m/merged_ghsl.tif"
# Read the raster file into R
ghsl_raster <- raster(ghsl_raster_path)

```

```{r}
# Display information about the raster
print(ghsl_raster)
```
```{r}
# Plot the raster
plot(ghsl_raster)
```

#!!!!!!The extract function!!!!!!!!!!!!!!!

```{r}
# function

# weighted sum per polygon (using the size of the pixel covered by the polygon "coverage_fraction")

extract_sum  <-  function(raster, polygon, field){

  polygon $id_tmp <- as.data.frame(polygon)[,field]

  v.exact <- exactextractr::exact_extract(raster, polygon, include_cols = 'id_tmp', max_cells_in_memory=3e+10)

  x <- do.call("rbind",v.exact)

  x[,"gpw"] <- x[, "value"] * x$coverage_fraction

  x_sum <- x %>%

    dplyr::group_by(id_tmp)%>%

    dplyr::summarise_at("gpw", sum, na.rm = TRUE)

polygon <- polygon %>%

    left_join(x_sum, by = "id_tmp")

  rm(x,v.exact,x_sum)

  return(polygon)

}
```


```{r}
# Data
sf_data <- st_read(url) 
polygon_camps <-sf_data

```


```{r}
raster_population <- rast('D:/EAGLE/Master_Thesis_Hannes/1/ghsl_pop_2020_mollweid_100m/merged_ghsl.tif')
```

```{r}
# Call function

polygon_camps <- extract_sum(raster_population, polygon_camps,"Name")

```


#Difference in the population
```{r}


# Subtract N_INDVID from ras_name
polygon_camps$ghsl_difference <- polygon_camps$N_INDVID - polygon_camps$ghsl

# View the resulting data frame with the new "difference" column
print(polygon_camps)

```
#Writing the output of the ghsl extract

```{r}

library(sf)

# Convert the data frame to an sf object
sf_polygon_camps <- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
sf_polygon_camps <- st_zm(sf_polygon_camps, drop = TRUE)

# Export the sf object to a shapefile
st_write(sf_polygon_camps,
 "ghsl_output/polygon_camps_ghsl.shp")

```
GHSL some plot visualisation

```{r}
library(ggplot2)



# Define the ggplot object
ggplot(polygon_camps, aes(fill = ghsl)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of GHSL Values for Camps") +
  theme_minimal()

```
```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = ghsl, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated and survey iom populations",
       x = "Estimated population",
       y = "Iom surveyed population") +
  theme_minimal()
```
```{r}
# Scatter plot with different colors based on Shelt_type
ggplot(polygon_camps, aes(x = ghsl, y = N_INDVID, color = Shelt_type)) +
  geom_point() +
  labs(title = "Comparison between ras_name and N_INDVID",
       x = "ras_name",
       y = "N_INDVID") +
  theme_minimal()
```

```{r}
# Scatter plot comparing N_INDIVID and N_HH
plot1 <- ggplot(polygon_camps, aes(x = N_INDVID, y = N_HH, color = ghsl)) +
  geom_point() +
  labs(title = "Comparison between N_INDVID and N_HH",
       x = "N_INDVID",
       y = "N_HH") +
  theme_minimal()

# Scatter plot comparing N_INDIVID and ras_name
plot2 <- ggplot(polygon_camps, aes(x = N_INDVID, y = ghsl, color = ghsl)) +
  geom_point() +
  labs(title = "Comparison between N_INDVID and ghsl",
       x = "N_INDVID",
       y = "ghsl") +
  theme_minimal()

# Scatter plot comparing N_HH and ras_name
plot3 <- ggplot(polygon_camps, aes(x = N_HH, y = ghsl, color = ghsl)) +
  geom_point() +
  labs(title = "Comparison between N_HH and ghsl",
       x = "N_HH",
       y = "ghsl") +
  theme_minimal()

# Arrange the plots in a grid
grid.arrange(plot1, plot2, plot3, ncol = 2)
```
#2.World POP(constrained)

```{r}
World_pop <- rast('D:/EAGLE/Master_Thesis_Hannes/1/world_pop/nga_ppp_2020.tif')
print(World_pop)
```


```{r}

# Call function

polygon_camps <- extract_sum(World_pop,polygon_camps,"Name")

```
#Difference in the survery_population and world_pop
```{r}
# Assuming you have a column named "N_INDVID" in the polygon_camps data frame
# Adjust the column name if needed

# Subtract N_INDVID from ras_name
polygon_camps$world_pop_difference <- polygon_camps$N_INDVID - polygon_camps$wp_c

# View the resulting data frame with the new "difference" column
print(polygon_camps)

```



#Writing the output of the worldpop unconstrained extract

```{r}
# Convert the data frame to an sf object
sf_polygon_camps2 <- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
sf_polygon_camps2 <- st_zm(sf_polygon_camps2, drop = TRUE)

# Export the sf object to a shapefile
st_write(sf_polygon_camps2,
 "world_pop_output/wp_c.shp")

```

#World pop constrained plots
```{r}
# Define the ggplot object
ggplot(polygon_camps, aes(fill = wp_c)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of GHSL Values for Camps") +
  theme_minimal()

```

```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = wp_c, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated_worldpop and survey iom populations",
       x = "Estimated population_worldpop",
       y = "Iom surveyed population") +
  theme_minimal()
```


#3.World POP(unconstrained)

```{r}
World_pop_unconstr <- rast('D:/EAGLE/Master_Thesis_Hannes/1/world_pop_build/nga_ppp_2020_constrained.tif')
print(World_pop_unconstr)

```

```{r}
# Call function

polygon_camps <- extract_sum(World_pop_unconstr,polygon_camps,"Name")

```

#Difference in the survery_population and world_pop unconstrained
```{r}


# Subtract N_INDVID from ras_name
polygon_camps$wp_uc_diff <- polygon_camps$N_INDVID - polygon_camps$wp_uc

# View the resulting data frame with the new "difference" column
print(polygon_camps)
```



#Writing the output of the worldpop unconstrained extract

```{r}
# Convert the data frame to an sf object
poly_camp3<- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
poly_camp3 <- st_zm(poly_camp3, drop = TRUE)

# Export the sf object to a shapefile
st_write(poly_camp3,
 "world_pop_uncons_output/polygon_wpun.shp")



```
#World pop unconstrained plots

```{r}
# Define the ggplot object
ggplot(polygon_camps, aes(fill = wp_uc)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of worldpop constrained Values for Camps") +
  theme_minimal()
```

```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = wp_uc, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated_worldpop_unconstrained and survey iom populations",
       x = "Estimated population_worldpop_unconstrained",
       y = "Iom surveyed population") +
  theme_minimal()
```

#4. GPW_V4

```{r}

gpw <- rast('D:/EAGLE/Master_Thesis_Hannes/1/gpw/gpw-v4-population-count-rev11_2020_30_sec_tif/gpw_v4_population_count_rev11_2020_30_sec.tif')
print(gpw)
```


```{r}
# Call function

polygon_camps <- extract_sum(gpw,polygon_camps,"Name")
```

#Difference in the survery_population and gpw_population
```{r}
# Assuming you have a column named "N_INDVID" in the polygon_camps data frame
# Adjust the column name if needed

# Subtract N_INDVID from ras_name
polygon_camps$gpw_diff <- polygon_camps$N_INDVID - polygon_camps$gpw

# View the resulting data frame with the new "difference" column
print(polygon_camps)
```


#Writing the output of the gpw

```{r}
# Convert the data frame to an sf object
poly_camp4<- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
poly_camp4 <- st_zm(poly_camp4, drop = TRUE)

# Export the sf object to a shapefile
st_write(poly_camp4,
 "gpw/polygon_gpw1.shp")



```
#Gpw plots

```{r}
# Define the ggplot object
ggplot(polygon_camps, aes(fill = gpw)) +
  geom_sf() +  # Plot the polygons
  scale_fill_viridis_c() +  # Choose a color scale (you can change to your preference)
  labs(title = "Zonal Statistics of worldpop constrained Values for Camps") +
  theme_minimal()
```

```{r}
# Scatter plot with site_status
ggplot(polygon_camps, aes(x = gpw, y = N_INDVID, color = Site_Statu)) +
  geom_point() +
  labs(title = "Comparison between estimated_gpw and survey iom populations",
       x = "Estimated population_gpw",
       y = "Iom surveyed population") +
  theme_minimal()
```
#Writing out the whole GHSL, Worldpop(cns),worldpop(uncons),gpw
```{r}
 #Convert the data frame to an sf object
camp_poly_pop<- st_as_sf(polygon_camps)

# Remove Z (3D) coordinates
camp_poly_pop <- st_zm(camp_poly_pop, drop = TRUE)

# Export the sf object to a shapefile
st_write(camp_poly_pop,
 "all_pop_output/camp_poly_pop.shp")


```


```{r}
# Select relevant columns
selected_columns <- polygon_camps %>%
  select(id_tmp, ghsl, wp_c, wp_uc, gpw, N_INDVID) %>%
  gather(key = "Variable", value = "Value", -id_tmp)

# Plot
ggplot(selected_columns, aes(x = id_tmp, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  labs(title = "Comparison of Population Variables",
       x = "Camp ID",
       y = "Population",
       fill = "Variable") +
  theme_minimal() +
  theme(axis.text.x)

)
```


#load the data with all the population output to an new variable
```{r}
output_path<-("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/all_pop_output/camp_poly_pop.shp")

output_poly<-st_read(output_path) 
head(output_poly)
```

#!!!5 loading the data from all the building stats

```{r}
build_stat_path<-("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/all_pop_output/build_stat_inc/build_stat_inc.shp")
build_stats_inc<-st_read(build_stat_path)
head(build_stats_inc)
```


#calculating the shape_area of the camp from the geometries of camp_polygons

```{r}

#Calculate the shape area for each camp polygon
build_stats_inc$cal_Shp_area <-st_area(build_stats_inc$geometry)

# Print or view the results
print(build_stats_inc[,c("Name", "cal_Shp_area","Site_Ar")])

# Remove 'units' from the columns
build_stats_inc$cal_Shp_area <- as.numeric(build_stats_inc$cal_Shp_area)
build_stats_inc$Site_Ar <- as.numeric(build_stats_inc$Site_Ar)

# Calculate the difference between 'Calculated_Shape_Area' and 'Site_Ar'
build_stats_inc$Area_Diff <- build_stats_inc$Site_Ar-build_stats_inc$cal_Shp_area

print(build_stats_inc[, c("Name", "cal_Shp_area","Site_Ar","Area_Diff")])
```





# write out the output with the polygon shapearea for surety

```{r}


# Export the sf object to a shapefile
st_write(build_stats_inc,
 "all_pop_output/build_stat_inc/build_stat_inc_c.shp")
```

#plot site area of the camps from survey and site area calculated from the digitized

```{r}
# Create a scatter plot
ggplot(build_stats_inc, aes(x = Site_Ar, y = cal_Shp_area)) +
  geom_point(aes(color = "cal_Shp_area"), size = 3) +
  geom_point(aes(color = "Site Area"), size = 1) +
  scale_color_manual(values = c("cal_Shp_area" = "blue", "Site Area" = "red")) +
  labs(title = "Survey_Site Area vs. Calculated Shape Area",
       x = "Survey_Site Area",
       y = "Calculated Shape Area")
```

#plot to check the problem of high population and less area

```{r}
# Create a scatter plot
ggplot(build_stats_inc, aes(x = N_INDVI, y = cal_Shp_area)) +
  geom_point() +
  labs(title = "N_INDVID vs. Calculated Shape Area",
       x = "N_INDVID",
       y = "Calculated Shape Area")
```

```{r}
# Filter camps with high N_INDVID and small cal_Shape_area
check_hipop_lessarea <- camps %>%
  filter(N_INDVI >50,Site_Ar<1000)

# Print or view the selected camps
print(check_hipop_lessarea[, c("Name", "N_INDVI", "cl_Shp_","Site_Ar","Site_nm")])
```


# the camp values(BO_S294 has the high population of 224 with less area of 342 sq m)
#  Name N_INDVI cal_Shp_area
<!-- 1  AD_S018    75.0   25822.0515 -->
<!-- 2  BO_S294   224.0     342.7668 -->
<!-- 3  AD_S003  1234.0  104062.6921 -->
<!-- 4  BO_S012  3375.0   17558.3622 -->
<!-- 5  BO_S015  1259.0   39288.4634 -->
<!-- 6  BO_S113  5708.0  256595.9877 -->
<!-- 7  BO_S114   739.0   10824.5435 -->
<!-- 8  BO_S160  2500.0  143393.6697 -->
<!-- 9  BO_S162  1260.0   40156.3581 -->
<!-- 10 BO_S203  9223.0  575925.1669 -->

#another filtering of population >50 and area <1000square gave 3 filters
1 BO_S294     224  342.7668  334.61 POLYGON ((13.19264 11.85126...
2 BO_S265     207 1015.6604  999.93 POLYGON ((13.13323 11.78958...
3 BO_S105     110  985.3237  934.06 POLYGON ((13.13257 11.79066...


# loading the data for with calculated shape area 

```{r}
build_stat_path2<-("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/all_pop_output/build_stat_inc/build_stat_inc_c.shp")
camps<-st_read(build_stat_path2)
head(camps)
```

#!!Attributes removing code
#!! Run only if needed
```{r}
# attributes_to_remove <- c("cl_Shp_r","Area_Dff");
# 
# # Remove specified attributes
# data1<- data1%>%select(-one_of(attributes_to_remove))

```


#Population density 

```{r}
# Calculate population density

camps$Site_Ar <- as.numeric(camps$Site_Ar)
camps$N_INDVI <- as.numeric(camps$N_INDVI)
camps$st_pp_d <- (camps$N_INDVI) / (camps$Site_Ar)

# Print the result
# Print or view the selected camps
print(camps[, c("Name", "N_INDVI", "Site_Ar","st_pp_d")])

```

#******plots for the eo datasets****************


#BOX+VIOLIN plot for the IOM survey population for different Site Type informal camps



```{r}
# Load the required library
library(ggplot2)
```


```{r}
# Create a boxplot for N_INDVI
plot_camp_pop <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = N_INDVI, fill = "N_INDVI"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Site Population", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = N_INDVI, fill = "N_INDVI",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site population from IOM survey for different Site Status", x = "Site Status", y = "Site Population") +
  geom_violin(aes(x = Sit_Stt, y = N_INDVI, fill = "N_INDVI"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)+
  #median pointed code if needed
  #  stat_summary(
  #   aes(x = Sit_Stt, y = as.numeric(N_INDVI), fill = "N_INDVI"),
  #   fun = median,
  #   geom = "point",
  #   shape = 23,
  #   size = 2,
  #   color = "black",
  #   position = position_dodge(width = 0.5)
  # )
  
  
 # !!!!if needed to display then have to run the median code below first 
  # geom_text(
  #   data = median_values,
  #   aes(x = Sit_Stt, y = median_ghsl, label = sprintf("%.1f", median_ghsl)),
  #   vjust = -1,
  #   size = 1,
  #   color = "black",
  #   hjust = 0.5
  # ) 
#   # Calculate median values for each Sit_Stt group
# median_values <- camps %>%
#   group_by(Sit_Stt) %>%
#   summarize(median_N_INDVI = median(as.numeric(N_INDVI)))
#   

# stat_summary(
  #   aes(x = Sit_Stt, y = as.numeric(N_INDVI)),
  #   fun = median,
  #   geom = "crossbar",
  #   width = 0.4,
  #   col = "red",
  #   show.legend = FALSE
  # )

print(plot_camp_pop)
```
#Analysis :
1.It is totally evident that the population in the informal survey sites are lesser than that of the formal survey sites
2.One of the outliers for the formal camps ranges greater than 4000 for the site population



#saving the N_INDVI plot 
```{r}
# Save the plot to a file
ggsave("plots/N_INDVI.png", plot = plot_camp_pop, width = 8, height = 6, dpi = 400)
```

#BOX+VIOLIN plot for the calculated ghsl population for classified as formal and informal camps


```{r}
# Create a boxplot for ghsl
ghsl_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(ghsl), fill = "ghsl"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated GHSL Population", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(ghsl), fill ="ghsl",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site population calculated from GHS POP  for different Site Status", x = "Site Status", y = "Calculated GHSL Population") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(ghsl), fill = "ghsl"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(ghsl_plot)
  
```
#saving the ghsl plot 
```{r}
# Save the plot to a file
ggsave("plots/ghsl_box.png", plot = ghsl_plot, width = 8, height = 6, dpi = 400)
```


#BOX+VIOLIN plot for the calculated Worldpop(Unconstrained) population for classified as formal and informal camps


```{r}
# Create a boxplot for wp_unconstrained
wp_u_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(wp_uc), fill = "wp_uc"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated worldpop Population(unconstrained)", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(wp_uc), fill ="wp_uc",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site population calculated from Worlpop(Unconstrained) for different Site Status", x = "Site Status", y = "Calculated worldpop Population(unconstrained)") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(wp_uc), fill = "wp_uc"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(wp_u_plot)
```

#saving the wp_uc plot 
```{r}
# Save the plot to a file
ggsave("plots/box_wp_uc.png", plot = wp_u_plot, width = 8, height = 6, dpi = 400)
```

#BOX+VIOLIN plot for the calculated Worldpop(constrained) population for classified as formal and informal camps

```{r}
# Create a boxplot for wp_constrained
wp_c_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(wp_c), fill = "wp_c"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated worldpop Population(Constrained)", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(wp_c), fill ="wp_c",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site population calculated from Worlpop(Constrained) for different Site Status", x = "Site Status", y = "Calculated worldpop Population(Constrained)") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(wp_c), fill = "wp_c"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(wp_c_plot)
```
#saving the wp_c plot 
```{r}
# Save the plot to a file
ggsave("plots/box_wp_c.png", plot = wp_c_plot, width = 8, height = 6, dpi = 400)
```

#BOX+VIOLIN plot for the calculated GPW population for different site status

```{r}
# Create a boxplot for wp_constrained
gpw_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(gpw), fill = "gpw"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated GPW population", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(gpw), fill ="gpw",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site population calculated from GPW data for different Site Status", x = "Site Status", y = "Calculated GPW population") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(gpw), fill = "gpw"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(gpw_plot)
```


#saving the gpw plot 
```{r}
# Save the plot to a file
ggsave("plots/box_gpw.png", plot =gpw_plot, width = 8, height = 6, dpi = 400)
```


#**BUILDING DATA PLOTS*************

#BOX+VIOLIN plot for number of households in Survey data  for different site status

```{r}
N_HHplot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(N_HH), fill = "N_HH"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Survey Household number", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(N_HH), fill ="N_HH",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site IOM surveyed household numbers", x = "Site Status", y = "Surveyed household number") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(N_HH), fill = "N_HH"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 7,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(N_HHplot)
```

#saving the google building count plot 
```{r}
# Save the plot to a file
ggsave("plots/N_HHplot.png", plot =N_HHplot, width = 8, height = 6, dpi = 400)
```



#BOX+VIOLIN plot for calculated buildings in Google building footprint data for different site status


```{r}
goog_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(g_b_c), fill = "g_b_c"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated Building count form GOOGLE data", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(g_b_c), fill ="g_b_c",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site building count calculated from Google building data for different Site Status", x = "Site Status", y = "Calculated Google building count") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(g_b_c), fill = "g_b_c"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 7,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(goog_plot)
```

#saving the google building count plot 
```{r}
# Save the plot to a file
ggsave("plots/box_goog.png", plot =goog_plot, width = 8, height = 6, dpi = 400)
```

#BOX+VIOLIN plot for calculated buildings in OSM building footprint data for different site status

```{r}
osm_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(osm_b_c), fill = "osm_b_c"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated Building count form Open Street Map data", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(osm_b_c), fill ="osm_b_c",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site building count calculated from Open Street map building data for different Site Status", x = "Site Status", y = "Calculated Open Street Map building count") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(osm_b_c), fill = "osm_b_c"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 7,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(osm_plot)
```
#saving the OSM building count plot 
```{r}
# Save the plot to a file
ggsave("plots/box_osm.png", plot =osm_plot, width = 8, height = 6, dpi = 400)
```

#BOX+VIOLIN plot for calculated buildings in Microsoft building footprint data for different site status

```{r}
msplot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(ms_b_c), fill = "ms_b_c"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated Building count form Microsoft data", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(ms_b_c), fill ="ms_b_c",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site building count calculated from Microsoft building data for different Site Status", x = "Site Status", y = "Calculated Microsoft building count") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(ms_b_c), fill = "ms_b_c"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 7,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(msplot)
```

#saving the Microsoft building count plot 
```{r}
# Save the plot to a file
ggsave("plots/box_ms.png", plot =msplot, width = 8, height = 6, dpi = 400)
```


#BOX+VIOLIN plot for calculated buildings in vida MS_gOOGLE data for different site status

```{r}
vida_plot <- ggplot(camps) + 
  geom_boxplot(aes(x = Sit_Stt, y = as.numeric(vid_b_c), fill = "vid_b_c"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Calculated Building count form Vida Google-Microsoft data", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = Sit_Stt, y = as.numeric(vid_b_c), fill ="vid_b_c",color = Sit_Stt), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Refugee site building count calculated from Vida Google-Microsoft building data for different Site Status", x = "Site Status", y = "Calculated Microsoft building count") +
  geom_violin(aes(x = Sit_Stt, y = as.numeric(vid_b_c), fill = "vid_b_c"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 7,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(vida_plot)
```


#saving the vida building count plot 
```{r}
# Save the plot to a file
ggsave("plots/box_vida.png", plot =vida_plot, width = 8, height = 6, dpi = 400)
```


