---
title: "urban_rural_grd3"
author: "Lallu Nikerthil Prathapan"
date: "3/10/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages library

```{r}
library(sf)
library(vctrs)
library(ggplot2)
library(raster)
library(exactextractr)
library(terra)
library(dplyr)
library(gridExtra)
library(tidyr)
library(units)
library(viridis)
library(hrbrthemes)
library(corrplot)
```



#5 loading the data from all the building stats

```{r}
build_stat_path<-("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/all_pop_output/camps_EO/camps_eo1.shp")
build_stats_inc<-st_read(build_stat_path)
head(build_stats_inc)
data_fr_ur<-build_stats_inc
```



#Categorising the urban, periurban, rural, hamlet from GRD3
#as data was so big did the clipping in qgis and expprted the clipped data here
WGS 84
```{r}
grd3_path<-"D:/EAGLE/Master_Thesis_Hannes/1/grd3_settlementextent/clipped/clipped_grd3.shp"
grd3<-st_read(grd3_path)
head(grd3)
```


#joining grd3 data to the camp_polygon dataset so far
#now trying to clip it
```{r}
# Perform a spatial intersection between camp_polygons and grid3_data

clipped_data <- st_intersection(grd3,build_stats_inc )

```



#Keeping only the dou1 an dou2 column for the urban to rural classifications in the data

```{r}
# Select only two columns from the clipped_data
selected_columns <- clipped_data[, c("dou_level1", "dou_level2")]
print(selected_columns)
```
# I removed all the other attributes from the grd3 after merging the data with the camp data so far using the code below
#!!!! Run once only
#Removing unnecessary attributes// only run if needed
```{r}
# attributes_to_remove <- c("smod.x","smod.y","smod");
# 
# # Remove specified attributes
# build_stats_inc<- build_stats_inc%>%select(-one_of(attributes_to_remove))

```

#now clipped data have urban classification, population from GHSL, Worlpop(constrained, unconstrained), GPW and the building data from google, !!!!!have to be addded microsoft, vida-google-microsoft, osm.

# writing out this data remembering now there is 226 number because of the repetation of  BN_S023, B0_S259,BO_S350


```{r}
# Write out the entire clipped_data to a GeoPackage (or other supported formats)
st_write(clipped_data, "D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/everything/all_merg.shp")
```
#**plots for grd3*******


```{r}
barplot_data <- clipped_data %>%
  group_by(dou_level1, status) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = dou_level1, y = count, fill = status)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = count), position = position_dodge(width = 0.9), vjust = -0.5) + # Add count labels
  labs(title = "Count of Formal and Informal Camps by dou_level1",
       x = "dou_level1",
       y = "Count",
       fill = "Status") +
  theme_minimal() +
  theme(axis.text.x = element_text( hjust = 1))+scale_fill_viridis(discrete=TRUE, name="") +coord_flip()

# Create a stacked bar plot showing the count of formal and informal camps for each dou_level2
stacked_barplot_data <- clipped_data %>%
  group_by(dou_level2, status) %>%
  summarise(count = n()) %>%
  ggplot(aes(x = dou_level2, y = count, fill = status)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = count), position = position_stack(vjust = 0.5), size = 3) + # Add count labels
  labs(title = "Count of Formal and Informal Camps by dou_level2",
       x = "dou_level2",
       y = "Count",
       fill = "Status") +
  theme_minimal() +
  theme(axis.text.x = element_text( hjust = 1))+scale_fill_viridis(discrete=TRUE, name="") +
  coord_flip()

# Show the bar plots
print(barplot_data)
print(stacked_barplot_data)
```
#saving the plot




```{r}
# Calculate counts of Sit_Stt for each dou_level1
count_data_dou_level1 <- clipped_data %>%
  group_by(dou_level1, Sit_Stt) %>%
  summarise(count = n())

# Create a bar plot showing the count of Sit_Stt for each dou_level1
barplot_dou_level1 <- ggplot(count_data_dou_level1, aes(x = dou_level1, y = count, fill = Sit_Stt)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = count), position = position_dodge(width = 0.9), vjust = -0.5) + # Add count labels
  labs(title = "Count of Refugee site status by Degree of Urbanisation(level-1) from GRD3 data",
       x = "dou_level1",
       y = "Count",
       fill = "Sit_Stt") +
  theme_minimal() +
  theme(axis.text.x = element_text(hjust = 1))+scale_fill_viridis(discrete=TRUE, name="") +
  coord_flip()

# Calculate counts of Sit_Stt for each dou_level2
count_data_dou_level2 <- clipped_data %>%
  group_by(dou_level2, Sit_Stt) %>%
  summarise(count = n())

# Create a stacked bar plot showing the count of Sit_Stt for each dou_level2
barplot_dou_level2 <- ggplot(count_data_dou_level2, aes(x = dou_level2, y = count, fill = Sit_Stt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = count), position = position_stack(vjust = 0.5), size = 3) + # Add count labels
  labs(title = "Count of Refugee site status by Degree of Urbanisation(level-2)in GRD3 data",
       x = "dou_level2",
       y = "Count",
       fill = "Sit_Stt") +
  theme_minimal() +
  theme(axis.text.x = element_text( hjust = 1))+scale_fill_viridis(discrete=TRUE, name="") +
  coord_flip()

# Show the bar plots
print(barplot_dou_level1)
print(barplot_dou_level2)
```

#saving the plots 
```{r}
# Save the plot to a file
ggsave("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/Plots/bar_grd3_st_stt1.png", plot =barplot_dou_level1, width = 8, height = 6, dpi = 400)
ggsave("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/Plots/bar_grd3_st_stt2.png", plot =barplot_dou_level2, width = 8, height = 6, dpi = 400)

```

#N_INDVI and dou_levels1(Boxplot try)
```{r}

# Create a boxplot for ghsl
d1_plot <- ggplot(clipped_data) + 
  geom_boxplot(aes(x = dou_level1, y = as.numeric(N_INDVI), fill = "N_INDVI"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Degree of urbanisation(level1)", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = dou_level1, y = as.numeric(N_INDVI), fill ="N_INDVI",color = dou_level1), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Degree of urbanisation-level1 from GRD3 data with site population", x = "Degree of urbanisatin(l1)", y = "Surveyed IOM population") +
  geom_violin(aes(x = dou_level1, y = as.numeric(N_INDVI), fill = "N_INDVI"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(d1_plot)
```

#saving the plot
```{r}
# Save the plot to a file
ggsave("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/Plots/box_N_IND_dou1.png", plot =d1_plot, width = 8, height = 6, dpi = 400)
```

#dou_level2_NINDVI
```{r}
# Create a boxplot for ghsl
d2_plot <- ggplot(clipped_data) + 
  geom_boxplot(aes(x = dou_level2, y = as.numeric(N_INDVI), fill = "N_INDVI"), alpha = 0.2, width = 0.5) +
  #scale_fill_viridis`(discrete = TRUE, alpha = 0.6) +
  scale_fill_viridis_d(name = "Degree of urbanisation(level2)", alpha = 0.6) +
  theme_ipsum()+
  geom_jitter(aes(x = dou_level2, y = as.numeric(N_INDVI), fill ="N_INDVI",color = dou_level2), size = 0.2, alpha = 0.9,show.legend = FALSE) +
  coord_flip() +
  labs(title = "Degree of urbanisation-level2 from GRD3 data with site population", x = "Degree of urbanisatin(l2)", y = "Surveyed IOM population") +
  geom_violin(aes(x = dou_level2, y = as.numeric(N_INDVI), fill = "N_INDVI"), alpha = 0.3) +
  
  theme(plot.title = element_text(size = 9,color="Blue",hjust=0.5),
        axis.title.x = element_text(size = 6,hjust = 0.5),
        axis.title.y=element_text(size = 6,hjust = 0.5),
        axis.text.x = element_text(size=5),
        axis.text.y=element_text(size = 5),
        )+ guides(fill = FALSE)

print(d2_plot)
```
#saving the plot
```{r}
# Save the plot to a file
ggsave("D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/Plots/box_N_IND_dou2.png", plot =d2_plot, width = 8, height = 6, dpi = 400)
```




#******************GHSL SMOD*********************

```{r}
smod_path<-("D:/EAGLE/Master_Thesis_Hannes/1/ghsl_settlement_extent/merged/mrgd_smod.tif")
smod<-raster(smod_path)
print(smod)
head(smod)
plot(smod)
```


#Need to change the projection to mollweid before that
```{r}
st_crs(data_fr_ur)
st_crs(smod)
# Convert to Mollweide projection (replace "Mollweide" with the desired projection)
data_fr_ur_gh<- st_transform(data_fr_ur, crs = "+proj=moll")
st_crs(data_fr_ur_gh)
```



```{r}
# Extract raster values for camp polygons
extracted_values <- raster::extract(smod, data_fr_ur_gh)

# Add the extracted values to the camp_polygons data frame
data_fr_ur_gh$extracted_values <- extracted_values

# Print or view the updated camp_polygons data frame
print(data_fr_ur_gh[, c("Name", "extracted_values")])
```
  
#The classed in smod (urban classification)
#The settlement grid at level 2 represents these definitions on a layer grid. Each pixel is classified as follow:
— Class 30: “Urban Centre grid cell”, if the cell belongs to an Urban Centre spatial entity;
— Class 23: “Dense Urban Cluster grid cell”, if the cell belongs to a Dense Urban Cluster spatial entity;
— Class 22: “Semi-dense Urban Cluster grid cell”, if the cell belongs to a Semi-dense Urban Cluster 
spatial entity;
— Class 21: “Suburban or per-urban grid cell”, if the cell belongs to an Urban Cluster cells at first 
hierarchical level but is not part of a Dense or Semi-dense Urban Cluster;
— Class 13: “Rural cluster grid cell”, if the cell belongs to a Rural Cluster spatial entity;
— Class 12: “Low Density Rural grid cell”, if the cell is classified as Rural grid cells at first hierarchical 
level, has more than 50 inhabitant and is not part of a Rural Cluster;
— Class 11: “Very low density rural grid cell”, if the cell is classified as Rural grid cells at first hierarchical 
level, has less than 50 inhabitant and is not part of a Rural Cluster;
— Class 10: “Water grid cell”, if the cell has 0.5 share covered by permanent surface water and is not 
populated nor built.


```{r}
# Write out the entire clipped_data to a GeoPackage (or other supported formats)
st_write(data_fr_ur, "D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/everything/u_r_smod.shp")
```
#realised that the region will remained clipped in the sections where there is no data and no way to change that

#**maps***

```{r}

# Convert extracted values to character
data_fr_ur_gh$extracted_values <- as.character(data_fr_ur_gh$extracted_values)

# Split the extracted values
extracted_values <- strsplit(data_fr_ur_gh$extracted_values, ", ")

# Convert to numeric
extracted_values <- lapply(extracted_values, function(x) as.numeric(x))

# Duplicate geometry to match the length of extracted values
duplicated_geometry <- rep(data_fr_ur_gh$geometry, lengths(extracted_values))

# Create a data frame with the extracted values and duplicated geometry
values_df <- data.frame(
  extracted_class = unlist(extracted_values),
  geometry = duplicated_geometry
)

# Convert extracted_class to factor with appropriate levels
values_df$extracted_class <- factor(values_df$extracted_class, levels = c("10", "11", "12", "13", "21", "22", "23", "30"))

# Convert to sf object
values_sf <- st_as_sf(values_df)

# Plot
ggplot() +
  geom_sf(data = values_sf, aes(fill = extracted_class)) +
  scale_fill_manual(values = c(
    "10" = "blue", "11" = "lightblue", "12" = "green", "13" = "yellow",
    "21" = "orange", "22" = "red", "23" = "darkred", "30" = "purple"
  ), name = "Extracted Class") +
  labs(title = "Extracted Values Map") +
  theme_minimal()
```


#zoom to any regions of extracted value
```{r}

# Define the extracted value you want to zoom in on
extracted_value_to_zoom <- "30"

# Filter the values_df dataframe for the extracted value
filtered_values_df <- subset(values_df, extracted_class == extracted_value_to_zoom)

# Convert the filtered dataframe to an sf object
filtered_values_sf <- st_as_sf(filtered_values_df)

# Plot the filtered sf object
ggplot() +
  geom_sf(data = filtered_values_sf, aes(fill = extracted_class)) +
  scale_fill_manual(values = c(
    "10" = "blue", "11" = "lightblue", "12" = "green", "13" = "yellow",
    "21" = "orange", "22" = "red", "23" = "darkred", "30" = "purple"
  ), name = "Extracted Class") +
  labs(title = paste("Zoomed in on Extracted Value:", extracted_value_to_zoom)) +
  theme_minimal()
```

# A scatter plot to visualise how the Site _status effec the urban-rural classification from the GHSL_SMOD data

```{r}
# Create a scatter plot
ggplot(data = data_fr_ur_gh, aes(x = extracted_values, y = Sit_Stt)) +
  geom_point(aes(color = Sit_Stt)) +
  scale_color_manual(values = c("Formal" = "blue", "Informal" = "red"), name = "Site Status") +
  labs(
    title = "Relationship between Extracted Value and Site Status",
    x = "Extracted Class",
    y = "Site Status"
  ) +
  theme_minimal()+coord_flip()
```

#trying the heat map

```{r}
# Coerce extracted values to character type
data_fr_ur_gh$extracted_values <- as.character(data_fr_ur_gh$extracted_values)

# Define representative labels for each category
category_labels <- c("10" = "Water", "11" = "Very low density rural", "12" = "Low density rural",
                     "13" = "Rural cluster", "21" = "Suburban or per-urban", "22" = "Semi-dense urban",
                     "23" = "Dense urban", "30" = "Urban Centre")

# Add a new column to data_fr_ur_gh with the representative labels
data_fr_ur_gh$extracted_label <- category_labels[data_fr_ur_gh$extracted_values]

# Create the heatmap with the generalized extracted values
heatmap_generalized <- ggplot(data_fr_ur_gh, aes(x = factor(Sit_Stt), y = extracted_label, fill = extracted_label)) +
  geom_tile() +
  scale_fill_manual(values = category_colors) +
  labs(
    title = "Heatmap of Generalized Extracted Values and Site Status",
    x = "Site Status",
    y = "Extracted Class"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels

# Print the generalized heatmap
print(heatmap_generalized)
```

