---
title: "urban_rural_grd3"
author: "Lallu Nikerthil Prathapan"
date: "3/10/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages library

```{r}
library(sf)
library(ggplot2)
library(raster)
library(exactextractr)
library(terra)
library(dplyr)
library(gridExtra)
library(tidyr)
library(units)
```



#5 loading the data from all the building stats

```{r}
build_stat_path<-("D:/EAGLE/Master_Thesis_Hannes/1/R/kml_gee/all_build_stats/all_build_stats.shp")
build_stats_inc<-st_read(build_stat_path)
head(build_stats_inc)
```



#Categorising the urban, periurban, rural, hamlet from GRD3
#as data was so big did the clipping in qgis and expprted the clipped data here

```{r}
grd3_path<-"D:/EAGLE/Master_Thesis_Hannes/1/grd3_settlementextent/clipped/clipped_grd3.shp"
grd3<-st_read(grd3_path)
head(grd3)
```


#joining grd3 data to the camp_polygon dataset so far
#now trying to clip it
```{r}
# Perform a spatial intersection between camp_polygons and grid3_data

clipped_data <- st_intersection(grd3,build_stats_inc )

```



#Keeping only the dou1 an dou2 column for the urban to rural classifications in the data

```{r}
# Select only two columns from the clipped_data
selected_columns <- clipped_data[, c("dou_level1", "dou_level2")]
print(selected_columns)
```
# I removed all the other attributes from the grd3 after merging the data with the camp data so far using the code below
#!!!! Run once only
#Removing unnecessary attributes// only run if needed
```{r}
attributes_to_remove <- c("country","iso","is_fp","prob_fp","mgrs","pcode","date");

# Remove specified attributes
clipped_data<- clipped_data%>%select(-one_of(attributes_to_remove))

```

#now clipped data have urban classification, population from GHSL, Worlpop(constrained, unconstrained), GPW and the building data from google, microsoft, vida-google-microsoft, osm.

# writing out this data remembering now there is 226 number because of the repetation of  BN_S023, B0_S259,BO_S350


```{r}
# Write out the entire clipped_data to a GeoPackage (or other supported formats)
st_write(clipped_data, "D:/EAGLE/Master_Thesis_Hannes/1/R/Lallu_thesis/everything/all_merg.shp")
```


#******************GHSL SMOD*********************

```{r}
smod_path<-("D:/EAGLE/Master_Thesis_Hannes/1/ghsl_settlement_extent/merged/mrgd_smod.tif")
smod<-raster(smod_path)
```

